### 2019-03-03 report/final-report.tex
added to list of acronyms and symbols

We have written
papers~\cite{bijective-synthesis,quotient-synthesis,symmetric-synthesis}
describing and evaluating our algorithms. We produced open-source 
code~\cite{GitHub} that implements those algorithms.  In this report,
we summarize our key methods, results, and findings, focusing
on the core algorithms for bijective synthesis and quotient synthesis.

@@

Despite their limitations, bijections and bijective synthesis form a
useful foundation on top of which more general transformations between
data sets may be built.  Hence, in the second half of our of project,
we extended the regular expression-based specifications of data types
with \emph{isomorphisms} between strings, also known as
\emph{quotients}.  To synthesize transformations between sets of
strings modulo isomorphisms, we generate canonizing functions followed
by bijections (using the original bijective synthesis algorithm).  The
so-called \emph{quotient lenses}~\cite{quotientlenses} we generate are capable of handling
``irrelevant'' differences between structures such as white space or
permutations of items in a row of data set and hence expand the set of
transformations our system can define significantly.  Finally, we explored the
synthesis of \emph{symmetric lenses}~\cite{symmetric-lenses} , again building upon the
bijective platform that we started with.  Symmetric lenses are able to
ignore arbitrary chunks of data in A when generating target data B,
and vice-versa.  For example, a serial number specific to one data set
may be ignored when we translate to a second.  Symmetric lenses
further expand the set of allowed transformations.

@@

\begin{figure}[t]
\includegraphics{qfigs/asts.eps}
\caption{AST node measurements for each of the three approaches
on each of the 10 non-bijective benchmark problems.
Benchmarks are sorted in order of increasing complexity as measured by
the number of AST nodes in the source and target format descriptions. 
QRE Synthesis requires far fewer AST nodes than the other
two approaches.}
%%\caption{Count of benchmark programs definable using a given AST count. We find
%%that it takes far fewer AST nodes to define benchmark lenses using QRE
%%synthesis than with Optician without QRE synthesis or without synthesis.}
\label{fig:asts}
\end{figure}

@@

\section{List of Symbols, Abbreviations, and Acronyms}
\begin{tabular}{ll}
  DARPA & Defense Advanced Research Project Agency \\
\end{tabular}

>>>>

We have written
papers~\cite{bijective-synthesis,quotient-synthesis,symmetric-synthesis}
describing and evaluating our algorithms. We produced open-source 
code~\cite{GitHub} that implements those algorithms.  In this report,
we summarize our key methods, results, and findings, focusing
on the core algorithms for bijective synthesis, quotient synthesis and
simple symmetric synthesis.

@@

Despite their limitations, bijections and bijective synthesis form a
useful foundation on top of which more general transformations between
data sets may be built.  Hence, in the second half of our of project,
we extended the regular expression-based specifications of data types
with \emph{isomorphisms} between strings, also known as
\emph{quotients}.  To synthesize transformations between sets of
strings modulo isomorphisms, we generate canonizing functions followed
by bijections (using the original bijective synthesis algorithm).  The
so-called \emph{quotient lenses}~\cite{quotientlenses} we generate are capable of handling
``irrelevant'' differences between structures such as white space or
permutations of items in a row of data set and hence expand the set of
transformations our system can define significantly.  Finally, we explored the
synthesis of \emph{symmetric lenses}~\cite{symmetric-lenses}, again building upon the
bijective platform that we started with.  Symmetric lenses are able to
ignore arbitrary chunks of data in A when generating target data B,
and vice versa.  For example, a serial number specific to one data set
may be ignored when we translate to a second.  Symmetric lenses
further expand the set of allowed transformations.

@@

\begin{figure}[t]
\centering
\includegraphics{qfigs/asts.eps}
\caption{AST node measurements for each of the three approaches
on each of the 10 non-bijective benchmark problems.
Benchmarks are sorted in order of increasing complexity as measured by
the number of AST nodes in the source and target format descriptions. 
QRE Synthesis requires far fewer AST nodes than the other
two approaches.}
%%\caption{Count of benchmark programs definable using a given AST count. We find
%%that it takes far fewer AST nodes to define benchmark lenses using QRE
%%synthesis than with Optician without QRE synthesis or without synthesis.}
\label{fig:asts}
\end{figure}

@@

\section{List of Symbols, Abbreviations, and Acronyms}
\begin{tabular}{p{1in}p{5in}}
  \ToDNFRegex{}         & An operation that converts regular   expressions into DNF form\\
  \ToLens{}             & An operation that converts a DNF lens to a
  lens \\
  $\equiv_S$, $\equiv_T$ & Equivalence relations on data matching
                           regular expressions $S$ and $T$
                           respectively \\
  \AnyOpt{}             & Mode for simple symmetric synthesis that ignores the information-theoretic metric \\ 
  AST     & Abstract syntax tree\\
  DARPA   & Defense Advanced Research Project Agency \\
  \CCOpt{}              & Mode for simple symmetric synthesis that
                          replace our information-theoretic cost metric with one where 
                          the cost of the lens is the number of disconnects plus the number
                          of merges.\\
  \DNFLens{}            & Lens in disjunctive normal form\\
  DNF                   & Disjunctive normal form\\
  \DNFRegex{}, \DNFRegexAlt{}  & Regular expression in disjunctive normal form\\
  \Examples{}           & Examples \\
  \FLOpt{}              & Mode for simple symmetric synthesis that
                          returns the first highest ranked lens found
                          by  \GreedySynth \\
  \Lens{}               & A lens \\
  \NROpt{}              & Mode for simple symmetric synthesis that
                          ignores all \SRequire annotations in the SRE specifications. \\
  \NSOpt{}              & Mode for simple symmetric syntehsis that
                          ignores all \Skip annotations in the SRE specifications. \\ 
  QRE                   & Quotient regular expression\\
  SRE                   & Stochastic regular expression\\
  \BRegex and \BRegexAlt & Regular expressions provided by the user\\
  \Regex{}, \RegexAlt{} & Regular expressions\\
  $S \Leftrightarrow T$ & Type of a lens that maps between data
                          described by regular expressions $S$ and $T$\\
  \SSOpt{}              & Full symmetric synthesis algorithm\\
  \SSNCOpt{}            & Symmetric synthesis algorithm without using a library of
    existing lenses.\\
  \BSOpt{}              & Bijective lens synthesis algorithm\\

\end{tabular}
